
%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{Second round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop, Kevin Giovanetti, Zein-Eddine Meziani)}


\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\section*{}

Dear Mohammad Hattawy,

We have read the updated version of the paper and find it significantly 
improved over the first version we read. There are still some comments we think 
you should address:

The new plot of the data versus t shows far more clearly the point you are 
trying to make about possible modification of the struck proton in 4He. We are 
a bit concerned however that it would not be clear to the reader that there is 
significant expected smearing of the t variable due to the Fermi motion of the 
initial proton. The question we have is whether horizontal error bars on your 
plot, which would include the bin width effects and the smearing of the t 
variable, could be added to make this explicitly clear to the reader.\\
   \textcolor{blue}{We used the kinematics of the photons to determine $t$ specifically
   in order to avoid such uncertainty linked to the initial proton kinematics (see 
   Appendix H of the analysis note for details). However, the paper was unclear on 
   the topic, we have changed Fig 1 and added a statement line 160-163 to clarify 
   this in the new version.}\\

There are still a number of English language issues in the paper:\\

\begin{enumerate}

\item  Abstract: "The $Q^2$, $x_b$ and t dependencies .... are compared with 
   the one on the free proton": Since dependencies is plural, replace "the one"
      with "those".\\
   \textcolor{blue}{Corrected.}


\item  Line 150: greater the 1 GeV -> greater than 1 GeV.\\
   \textcolor{blue}{Corrected.}


\item  Line 152: formula would be $W^2 = (q+p)^2$, or else take square root.\\
   \textcolor{blue}{Corrected.}

   
\item  Line 218,219:  Three times misspelling of "integrated"\\
   \textcolor{blue}{Corrected.}

   
\item  Line 231: dependencies -> dependency\\
   \textcolor{blue}{Corrected.}

   
\item  Line 240: such as long-range interactions -> such as long-range 
   interactions and final state interactions of the knock-out proton.\\
   \textcolor{blue}{Corrected.}

\item  line 273: Sentence should be rewritten. Minimal suggesion:
"This surprising result opens a new avenue for progress in understanding the 
      properties of quarks and gluons in the nuclear medium.\\
   \textcolor{blue}{Corrected.}


\item  Caption to Figure 5: On the bottom -> On the bottom plot:
(positron beam was used) -> (a positron beam was used)\\
   \textcolor{blue}{Corrected.}


\item  References: line 343:  Accent on name:  R. Dupr\'{e}.\\
   \textcolor{blue}{Corrected.}

   

  
\end{enumerate}


\end{document}
