\bibliographystyle{unsrt}
\begin{thebibliography}{99}


% nuclear DVCS

\bibitem{M_Polyakov}
M. V. Polyakov, Generalized parton distributions and strong forces inside nucleons and nuclei, Phys. Lett. B 555, 57-62, 2003.

\bibitem{EMC_simonetta}
S. Liuti and K. Taneja, Nuclear Medium Modifications of Hadrons from Generalized Parton Distributions, Phys. Rev. C 72, 034902; arXiv:0504027v2 [hep-ph], 2005.

\bibitem{Kir}
A. Kirchner and D. M{\"u}ller, Deeply virtual Compton scattering off nuclei, Eur. Phys. J. C32, 347-375, 2003. 

\bibitem{BM_2009}
A. V. Belitsky and D. M{\"u}ller, Refined analysis of photon leptoproduction 
off spinless target, Phys. Rev. D79, 014017; arXiv:0809.2890 [hep-ph], 2009. 

\bibitem{Van}
M. Vanderhaeghen, Gauge invariance of DVCS off an arbitrary spin hadron: the deuteron target case, Eur. Phys. J. A 8, 455, 2000.

\bibitem{simonetta_pre}
S. Liuti, Exploring the transverse partonic structure of nuclei, Workshop on Hard Processes in Nuclei, ECT*, Trento, June 8-12, 2015.


\bibitem{He_4_FF_Frosch}
R. F. Frosch et al., Structure of the He-4 Nucleus from Elastic Electron Scattering, Phys. Rev. 160, 874, 1967.

\bibitem{He_4_FF}
A. Camsonne et al. (Jefferson Lab Hall A Collaboration), JLab Measurement of the $^4$He Charge Form Factor at Large Momentum Transfers, Phys. Rev. Lett. 112, 132503, 2014.

\bibitem{proposal}
K. Hafidi et al., Deeply virtual Comton scattering off $^4He$, JLab proposal to PAC 33, 2007.

\bibitem{EMC_vadim_1}
V. Guzey and M. Strikman, DVCS on spinless nuclear targets in impulse approximation, Phys. Rev. C 68, 015204; arXiv:0301216 [hep-ph], 2003.

\bibitem{EMC_vadim_3}
V. Guzey, Neutron contribution to nuclear DVCS asymmetries, Phys. Rev. C 78, 025211; arXiv: 0801.3235 [nucl-th], 2008.

\bibitem{free_proton_GPDs}
I. V. Musatov and A. V. Radyushkin, Evolution and models for skewed parton distributions, Phys. Rev. D 61, 074027, 2000


\bibitem{guidal_2}
M. Guidal et al., Generalized Parton Distributions in the valence region from Deeply Virtual Compton Scattering, arXiv:1303.6600v1 [hep-ph], 2013.

\bibitem{EMC_vadim_2}
V. Guzey, A.W. Thomas and K. Tsushima, Medium modifications of the bound nucleon GPDs and incoherent DVCS on nuclear targets, Phys. Lett. B 673, 9-14; arXiv:0806.3288 [nucl-th], 2009. 
 

\bibitem{QMC}
D. H. Lu et al., In-medium electron-nucleon scattering, Phys. Lett. B 417, 217, 1998.

\bibitem{simonetta_2}
S. Liuti and K. Taneja, Microscopic Description of Deeply Virtual Compton Scattering off Spin-0 Nuclei, Phys.Rev. C 72, 032201; arXiv:0505123v1 [hep-ph], 2005.

\bibitem{He4_DIS_data}
J. Gomez et al., Measurement of the A-dependence of deep inelastic electron
scattering. Phys. Rev. D 49, 4348-4372, 1994.

\bibitem{HERMES_BSA}
A. Airapetian et al. (HERMES Collaboration), Nuclear-mass dependence of beam-helicity and beam-charge azimuthal asymmetries in DVCS, Phys. Rev. C 81, 035202, 2010.


\bibitem{CLASref}
B.A. Mecking et al., The CEBAF large acceptance spectrometer, Nucl. Inst. and Meth. A 503, 513-553, 2003.


\bibitem{DCref}
M.D. Mestayer et al., The CLAS drift chamber System, Nucl. Inst. and Meth. A 449, 81, 2000.

\bibitem{CCref}
G. Adams et al., The CLAS Cerenkov detector, Nucl. Inst. and Meth. A 465, 414, 2001.

\bibitem{TOFref}
   E.S. Smith et al., The time-of-flight system for CLAS, Nucl. Inst. and Meth.  
   A 432, 265, 1999.

\bibitem{ECref}
   M. Amarian et al., The CLAS forward electromagnetic calorimeter, Nucl. Inst.  
   and Meth. A 460, 239, 2001.



\bibitem{Hyon-suk}
Hyon-Suk Jo, Etude de la Diffusion Compton Profond{\'e}ment Virtuelle Sur le Nucl{\'e}on avec le D{\'e}tecteur CLAS de Jefferson Lab: Mesure des Sections Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis, 2007. 


\bibitem{BONUS}
S. Tkachenko et al., Measurement of the nearly free neutron structure function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering with CLAS, Phys. Rev. C 89, 045206, 2014.

\bibitem{DME}
The PubChem Project. USA: National Center for Biotechnology Information, dimethyl ether - PubChem Public Chemical Database,  \url{http://pubchem.ncbi.nlm.nih.gov/compound/8254}. 

\bibitem{BONUS_2}
N. Baillie et al., BoNus Experiment Analysis Note, CLAS internal analysis note, 
\url{https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf}

\bibitem{GEM_holes}
J. Beringer et al. (Particle Data Group), Particle detectors at accelerators, Phys. Rev. D 86, 010001, pages: 339-368, 2012.

\bibitem{MAGBOLTZ}
S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting gases under the influence of electric and magnetic fields, Nucl. Inst. and Meth. in Phy. Res. A 421, pp. 234-240, 1999.

\bibitem{NATHAN}
N. Baltzell, New TPC Noise Reduction, \url{https://clasweb.jlab.org/rungroups/lowq/wiki/index.php/New_TPC_Noise_Reduction}


\bibitem{Osipenko}
M. Osipenko et al., Matching between the electron candidate track and the Cherenkov counter hit, CLAS-NOTE-020, 2004.

\bibitem{bethe_block}
J. Beringer et al. (Particle Data Group), Electronic energy loss by heavy particles, Phys. Rev. D 86, 010001, 2012.

\bibitem{FX_thesis}
F.X. Girod, Diffusion Compton profond{\'e}ment virtuelle avec le d{\'e}tecteur CLAS pour une {\'e}tude des distributions de partons g{\'e}n{\'e}ralis{\'e}es, Ph.D-Thesis, 2006.

\bibitem{fermi_motion}
C.Ciofi degli Atti and S.Simula, Realistic model of the nucleon spectral 
function in few- and many-nucleon systems, Phys. Rev. C 53, 1689.

\bibitem{GSIM}
CLAS collaboration, CLAS GEANT3 simulation,  \url{http://nuclear.unh.edu/~maurik/gsim_info.shtml}.

\bibitem{yohann}
Y. Perrin, Etude de la structure partonique du noyau d'h$\'e$lium, Ph.D thesis, 2012.

\bibitem{cristina}
C. Moody and N. Baltzell, IC depth corrections for CLAS-EG6 experiment,  \url{https://clasweb.jlab.org/rungroups/lowq/wiki/index.php/IC_Depth_Correction_Investigation_Creating_a_new_depth_correction
}.


\bibitem{FX_BSA}
F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries, Phys. Rev. Lett. 100, 162002, 2008.

\bibitem{CLAS_cross_section}
H.S. Jo et al. (CLAS Collaboration), Cross sections for the exclusive photon electroproduction on the proton and Generalized Parton Distributions, arXiv:1504.02009v1 [hep-ex], 2015.

\bibitem{Baptiste}
B. Guegan, Study of Generalized Parton Distributions and Deeply Virtual Compton Scattering on the nucleon with the CLAS and CLAS12, Ph.D-thesis, 2013.

\bibitem{Niki}
N. Saylor, A Measurement of Unpolarized Cross Sections and Polarized Cross Section Differences of Deeply Virtual Compton Scattering on the Proton at Jefferson Laboratory using CLAS, Ph.D-thesis, 2013.


\bibitem{hallb_polarimeter}
J. M. Grames et al., Unique electron polarimeter analyzing power comparison and precision spin-based energy measurement, Phys. Rev. Spec. Topics - Accelerators and Beams, Vol.7 , 042802, 2004.

\bibitem{Afanasev}
A.V. Afanasev, M.I. Konchatnij and N.P. Merenkov, Single-spin asymmetries in the Bethe-Heitler process $e^{-} + p \rightarrow  e^{-} + \gamma + p$ from QED radiative corrections, J. of Exp. and Theo. Phys. 102(2), 220-233, 2006.

\bibitem{EMC_vadim_4}
Private communication with V. Guzey based on his model presented in \cite{EMC_vadim_3}. 


\bibitem{eg1dvcs_photonenergy}
EG1-DVCS TN027, \url{https://clasweb.jlab.org/rungroups/eg1-dvcs/wiki/index.php/Technical_Notes}.

\bibitem{eg6beamoffset}
RTPC Alignment Calibration for EG6, CLAS-NOTE 2013-007, \url{https://misportal.jlab.org/ul/Physics/Hall-B/clas/viewFile.cfm/2013-007.pdf?documentId=705}.

\bibitem{eg6tpcoffset}
Beam XY-Position at the Target for CLAS/EG6, CLAS-NOTE 2013-008, \url{https://misportal.jlab.org/ul/Physics/Hall-B/clas/viewFile.cfm/2013-008.pdf?documentId=711}.


\bibitem{FX_analysis_note}
F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply Virtual Compton 
Scattering Beam-Spin Asymmetries, CLAS Note, 2007-026, 2007.

\bibitem{GPD_cal_free_p}
K. Kumericki, S. Liuti, H. Moutarde, GPD phenomenology and DVCS fitting - 
Entering the high-precision era, arXiv:1602.02763 [hep-ph], 2016.

\end{thebibliography}
